---
Title: "UBCO CSC Workshop Materials"
pagetitle: "UBCO CSC Workshop Materials"
output:
  html_document:
    includes:
      in_header: header.html
---
```{r, setup, include = F}
knitr::opts_chunk$set(
  echo = F,
  warning = F,
  message = F
)
```


# Research Data Hub

## Data Consultations

Our staff specialize in a variety of approaches for working with research data including Python, R, etc. for data visualization, modelling, statistical analysis, and many other topics related to preparing and analyzing research data from a broad spectrum of disciplines. Drop-in and bookable consultations available to those with all levels of experience.

To learn more and book a consult, visit: https://csc.ok.ubc.ca/consultations/research-data-consultation/

## Workshop Materials

```{r, workshops, results = 'asis'}
workshops <- read.csv("files/workshops.csv", header = T)

for (i in 1:nrow(workshops)) {
  title <- workshops[i,1]
  series <- workshops[i,2]
  description <- workshops[i,3]
  url <- workshops[i,4]
  cat('<a href="',url,'" target = "blank"><button class="landingPageButton"><h2>',title,'</h2><h3>Series: ',series,'</h3><p>',description,'</p></button></a>')
}
```