---
Title: "UBCO Research Data Hub"
pagetitle: "UBCO Research Data Hub"
output:
  html_document:
    includes:
      in_header: header.html
---
```{r, setup, include = F}
knitr::opts_chunk$set(
  echo = F,
  warning = F,
  message = F
)
```

## Data Consultations

Our staff specialize in a variety of approaches for working with research data including Python, R, etc. for data visualization, modelling, statistical analysis, and many other topics related to preparing and analyzing research data from a broad spectrum of disciplines. Drop-in and bookable consultations available to those with all levels of experience.

To learn more and book a consult, visit: https://csc.ok.ubc.ca/consultations/research-data-consultation/

## R & Python Blog

The [R & Python Blog](https://csc-ubc-okanagan.github.io/R-Python-Blog/) addresses common data issues and data analysis tasks.

The blog posts here were created by Research Data Consultants. If you find yourself with a question that has not been answered by the blog posts currently available, feel free to reach out to schedule a one-on-one consultation.

## Workshops

Workshop materials are available at https://csc-ubc-okanagan.github.io/workshops/

```{r, workshops, results = 'asis'}
workshops <- read.csv("files/workshops.csv", header = T)
cat('<table><tbody><tr><th>Title</th><th>Series</th><th>Description</th></tr>')
for (i in 1:nrow(workshops)) {
  title <- workshops[i,1]
  series <- workshops[i,2]
  description <- workshops[i,3]
  url <- workshops[i,4]
  cat('<tr><td>',title,'</td><td>',series,'</td><td>',description,'</td></tr>')
}
cat('</tbody></table>')
```